---
title: "Drone Recapture Simulation"
author: "Rex Macey"
date: "2/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = "")
```

```{r initialize}
source("droneRecaptureSimulation.r")
```

## Introduction

Do drones return to the same DCA?  That question leads us to estimate the probability of recapturing a drone assuming they do. If a researcher captures, marks and releases drones in a DCA, what is the probability what is the probability she will recapture a drone if she returns on a subsequent day?  

## Assumptions

Number of Drones Per DCA: `r nPerDCA`    
Number Captured Per Session: `r nCapturedPerSession`    
Number of Days To Mate:  `r nDaysToMate` (example days 12-32 would be 21)    
Minutes Flight Time:  `r minutesFlightTime` To travel to and from and stay in DCA    
Miles To DCA: `r milesToDCA` used to calculate time, probability of a drone being at a DCA  
Flight MPH: `r flightMPH` used to calculate time, probability of a drone being at a DCA  
Minutes Rest Time: `r minutesRestTime` used to calculate time, probability of a drone being at a DCA  
Flights Per Day: `r flightsPerDay` 
NumberDCAsVisited: `r numberDCAsVisited`
daysActive <- c(1,2,3,8,9,10) # Days researcher is actively capturing drones.  Should start at 1. Might skip days for bad weather.

## Intermediate Calculations
Minutes At DCA: `r minutesAtDCA` per trip from hive

## Simulation Description   
On first day of simulation there are _`r nPerDCA`_ drones in a DCA.  These drones will be of various ages.  Each drone is assigned a (uniform) random number from 1 to _`r nDaysToMate`_ representing its mating day.  After the last mating day is reached, the drone dies (in simulation, no drones were actually injured in this simulation).  