---
title: "Drone Recapture Simulation"
author: "Rex Macey"
date: "2/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = "", message = FALSE, warning = FALSE)
```

```{r initialize}
source("droneRecaptureSimulation.r")
```

## Introduction

A researcher is interested whether drones visit different DCAs.  She plans to visit `r nDCAsVisitedByKeeper` DCAs over 
`r daysInSimulation` visting on days `r daysActive[daysActive!=0]`. During a visit she will capture bees, paint them with a mark identifying the DCA, and release them.  This simulation attempts to address the question - is she likely to recapture drones at a DCA who were already captured at a different DCA? We use a Monte Carlo simulation.

## Assumptions
The number of drones is not a direct input.  To arrive at that figure, we assume about `r nPerDCA` drones will be at a DCA at any point in time.  Drones will visit `r nDCAsVisited` DCAs. The DCA a drone visits is randomly selected.  They visit a DCA for 30 minutes and rest for 15, meaning they are at a DCA two-thirds of the time. Thus to have `r nPerDCA` drones at `r nDCAsVisited` DCAs we will need `r nDrones` drones because `r nDrones` / `r nDCAsVisited` * 2/3 = `r nPerDCA`.  A drone is assumed to have `r nDaysToMate` days to mate (period of fertility).


We assume the researcher visits `r nDCAsVisitedByKeeper` DCAs on the days she can (e.g. weather permitting). She captures `r nCapturedPerFlight` drones on each flight of her UAV.  She is able to make 1 flight every 15 minutes.

## Simulation Description 
A day is divided into `r periodsPerDay` periods of 15 minutes. Initially each drone is randomly assigned an age of fertility (from 1 to `r nDaysToMate`).  They are also assigned to a DCA or to rest for each period. They are at a random DCA for 2 periods and rest for 1 period.  

On a day the researcher is active, she divides her attention among the same `r nDCAsVisitedByKeeper` DCAs.  She collects drones. She counts them as recaptured if they have already been marked as having been to a different DCA.  If they are unmarked, they are marked.

At the end of the day, the drones are aged a day.  If the drone is no longer fertile, he is replaced by an unmarked bee who is at the beginning of his period of fertility.

### Results
The simulation was repeated `r nTrials` times.  The following table summarizes the number of drones recaptured on a given day where recapture is defined as a drone previous captured at a different DCA.

```{r results}
summary(simResults)
```

